---
title: "election_data"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Adrian D. Garcia"
date: "September 2020"
output:
  html_document:
    toc: true
    toc_float: true
---

# Intro

## Getting Started

```{r setup, message = FALSE, warning = FALSE}

library(tidyverse) #For Data Analysis
library(lubridate) #For working with dates
library(DT) #For visualizing tables

```

I've downloaded individual contributions for the CEOs of the 15 largest fund shops using the FEC [websites](https://www.fec.gov/data/receipts/individual-contributions). The files were saved individually in the *indiv_09082020* folder. They were combined used **Combine.r**.

The data was pulled Sept. 8.

I used **working1.r** to add committee information to the CEO file. I pull in the result below.

```{r load, message = FALSE}

Data <- read_csv("FEC/CEO_FEC_09242020.csv")

```

I then create two new columns. The first (CEO) determines whether the contributor is a CEO or the spouse of a CEO. The second (COMPANY) standardizes what company the contributor works for.

```{r adjust, message = FALSE}

Adj_Data <- Data %>%
  mutate(
    CEO =
      case_when(
        name %in% c(
          "abigail johnson",
          "dana emery",
          "david butler",
          "douglas sieg",
          "gerard oreilly",
          "jennifer johnson",
          "laurence fink",
          "martin flanagan",
          "mary callahan erdoes",
          "michael falcon",
          "michael roberge",
          "mortimer buckley",
          "roger ferguson",
          "tim armour",
          "william stromberg",
          "william truscott"
        ) ~ "CEO",
        TRUE ~ "Spouse"
      ),
    COMPANY =
      case_when(
        grepl("AMERICAN FUNDS", contributor_employer) ~ "Capital Group/American Funds",
        grepl("AMERIPRISE", contributor_employer) ~ "Columbia Threadneedle",
        grepl("AMVESCAP PLC", contributor_employer) ~ "Invesco",
        grepl("INVESCO", contributor_employer) ~ "Invesco",
        grepl("BLACKROCK", contributor_employer) ~ "BlackRock",
        grepl("CAPITAL GROUP", contributor_employer) ~ "Capital Group/American Funds",
        grepl("CAPITAL RESEARCH", contributor_employer) ~ "Capital Group/American Funds",
        grepl("COLUMBIA", contributor_employer) ~ "Columbia Threadneedle",
        grepl("DIMENSIONAL FUND", contributor_employer) ~ "Dimensional Funds",
        grepl("FIDELITY", contributor_employer) ~ "Fidelity",
        grepl("FMR LLC", contributor_employer) ~ "Fidelity",
        grepl("FRANKLIN", contributor_employer) ~ "Franklin",
        grepl("JACKSON NATIONAL", contributor_employer) ~ "Jackson National",
        grepl("JPMORGAN", contributor_employer) ~ "JPMorgan",
        grepl("Abb[oe]tt", contributor_employer, ignore.case = TRUE) ~ "Lord Abbett",
        grepl("M.F.S.", contributor_employer) ~ "MFS",
        grepl("MFS", contributor_employer) ~ "MFS",
        grepl("PRUDENTIAL PLC", contributor_employer) ~ "Jackson National",
        grepl("ROWE PRICE", contributor_employer) ~ "T Rowe Price",
        grepl("TIAA", contributor_employer) ~ "TIAA",
        grepl("VANGUARD", contributor_employer) ~ "Vanguard",
        TRUE ~ contributor_employer
      )
  )

```

Here is a look at the name of the CEO, the standardized employer, and their original employer in the FEC data.

```{r adjust_view, echo=FALSE}

Adj_Data %>%  
  filter(CEO == "CEO") %>% 
  group_by(name, COMPANY, contributor_employer) %>% 
  summarise() %>% 
  datatable()

```

This a breakdown of what type of political group CEOs gave to in 2020.

```{r breakdown_view, echo=FALSE}

Adj_Data %>%  
  filter(CEO == "CEO" &
           two_year_transaction_period == "2020") %>% 
  group_by(name, committee_type) %>% 
  summarise(Sum_Contributions = sum(contribution_receipt_amount)) %>% 
  ggplot(data = ., mapping = aes(x = name, y = Sum_Contributions, fill = committee_type)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  scale_y_continuous(limits = c(0, 35000)) +
  ggtitle("Contributions During 2020 CYCLE") +
  ylab("2019-2020 Contributions") +
  xlab("CEOs") +
  theme_classic() +
  theme(plot.title = element_text(size = 11, face = "bold"))

```

2020

```{r 2020, echo=FALSE}

Couple_Sum_2020 <- Adj_Data %>% 
  select(name, spouse, CEO, committee_name, committee_type, two_year_transaction_period, contribution_receipt_amount) %>% 
  mutate(Couple = case_when(CEO == "CEO" ~ name,
                       TRUE ~ spouse)) %>% 
  group_by(Couple, two_year_transaction_period) %>% 
  summarise(TOTAL = sum(contribution_receipt_amount)) %>% 
  filter(two_year_transaction_period == "2020")

Couple_Breakdown_2020 <- Adj_Data %>% 
  select(name, spouse, CEO, committee_name, committee_type, two_year_transaction_period, contribution_receipt_amount) %>% 
  mutate(Couple = case_when(CEO == "CEO" ~ name,
                       TRUE ~ spouse)) %>% 
  group_by(Couple, committee_type, two_year_transaction_period) %>% 
  summarise(TOTAL = sum(contribution_receipt_amount)) %>% 
  filter(two_year_transaction_period == "2020") %>% 
  ungroup() %>% 
  mutate(
    committee_type =
      case_when(
        committee_type == "REP" ~ "REP",
        committee_type == "DEM" ~ "DEM",
        committee_type == "Company Pac" ~ "Company Pac",
        committee_type == "ICI Pac" ~ "ICI Pac",
        TRUE ~ "Other"
      )
  )

Indiv_Sum_2020 <- Adj_Data %>% 
  select(name, spouse, CEO, committee_name, committee_type, two_year_transaction_period, contribution_receipt_amount) %>% 
  group_by(name, spouse, two_year_transaction_period) %>% 
  summarise(TOTAL = sum(contribution_receipt_amount)) %>% 
  filter(two_year_transaction_period == "2020")

```


Historical

```{r historical, echo=FALSE}

Couple_Breakdown <- Adj_Data %>%
  select(
    name,
    spouse,
    CEO,
    committee_name,
    committee_type,
    two_year_transaction_period,
    contribution_receipt_amount
  ) %>%
  mutate(
    committee_types =
      case_when(
        committee_type == "REP" ~ "REP",
        committee_type == "DEM" ~ "DEM",
        committee_type == "Company Pac" ~ "Company Pac",
        committee_type == "ICI Pac" ~ "ICI Pac",
        TRUE ~ "Other"
      ),
    Couple =
      case_when(
        CEO == "CEO" ~ name,
        TRUE ~ spouse
        ),
    Order =
      case_when(
        committee_types == "REP" ~ 1,
        committee_types == "DEM" ~ 2,
        committee_types == "Company Pac" ~ 3,
        committee_types == "ICI Pac" ~ 4,
        committee_types == "Other" ~ 5
      )) %>%
  group_by(Couple, committee_type, committee_types, Order, two_year_transaction_period) %>%
  summarise(TOTAL = sum(contribution_receipt_amount)) %>%
  filter(two_year_transaction_period != "2020")

Spread <- Couple_Breakdown %>% 
  ungroup() %>% 
  select(1,3,5,6) %>% 
  pivot_wider(data = ., names_from = committee_types, values_from = TOTAL) %>% 
  select(1,2,5,4,3,7,6)


  ggplot(
    data = Couple_Breakdown,
    mapping = aes(x = as.character(two_year_transaction_period),
                  y = TOTAL,
                  fill = reorder(committee_types, -Order)
    )) +
  geom_bar(stat = "identity", position = "stack") +
  facet_wrap(~Couple, scales = "free") +
  ggtitle("Contributions During 2020 CYCLE") +
  ylab("2019-2020 Contributions") +
  xlab("CEOs") +
  theme_classic() +
  theme(plot.title = element_text(size = 11, face = "bold"))

```
TK

```{r TK, message=FALSE}

a <- Adj_Data %>%
  select(
    name,
    spouse,
    CEO,
    committee_name,
    committee_type,
    two_year_transaction_period,
    contribution_receipt_amount
  ) %>%
  mutate(
    committee_types =
      case_when(
        committee_type == "REP" ~ "REP",
        committee_type == "DEM" ~ "DEM",
        committee_type == "Company Pac" ~ "Company Pac",
        committee_type == "ICI Pac" ~ "ICI Pac",
        TRUE ~ "Other"
      ),
    Couple =
      case_when(
        CEO == "CEO" ~ name,
        TRUE ~ spouse
        ),
    Order =
      case_when(
        committee_types == "REP" ~ 1,
        committee_types == "DEM" ~ 2,
        committee_types == "Company Pac" ~ 3,
        committee_types == "ICI Pac" ~ 4,
        committee_types == "Other" ~ 5
      )) %>%
  # group_by(Couple, committee_type, committee_types, Order, two_year_transaction_period) %>%
  # summarise(TOTAL = sum(contribution_receipt_amount)) %>%
  filter(two_year_transaction_period != "2020")



b <- Adj_Data %>% 
  mutate(
    committee_types =
      case_when(
        committee_type == "REP" ~ "REP",
        committee_type == "DEM" ~ "DEM",
        committee_type == "Company Pac" ~ "Company Pac",
        committee_type == "ICI Pac" ~ "ICI Pac",
        TRUE ~ "Other"
      ),
    Couple =
      case_when(
        CEO == "CEO" ~ name,
        TRUE ~ spouse
        ),
    Order =
      case_when(
        committee_types == "REP" ~ 1,
        committee_types == "DEM" ~ 2,
        committee_types == "Company Pac" ~ 3,
        committee_types == "ICI Pac" ~ 4,
        committee_types == "Other" ~ 5
      )) %>% 
  
  
  
  filter(
    grepl("Hillary", committee_name, ignore.case = TRUE) |
     grepl("Obama", committee_name, ignore.case = TRUE) |
     grepl("Trump", committee_name, ignore.case = TRUE) |
      grepl("Pence", committee_name, ignore.case = TRUE) |
     grepl("Romney", committee_name, ignore.case = TRUE) |
     grepl("McCain", committee_name, ignore.case = TRUE) |
      grepl("Ryan", committee_name, ignore.case = TRUE) |
       grepl("Biden", committee_name, ignore.case = TRUE) |
       grepl("Kain", committee_name, ignore.case = TRUE) |
       grepl("Palin", committee_name, ignore.case = TRUE)
  )



```
